Deep Neural Networks for Bilingual Lexicon Extraction

### 2014-06-07 paper/main.tex
Minor formatting changes

\newcite{mikolov2013exploiting} found that a linear model could learn a
translation mapping between two monolingual vector spaces. We construct such a
linear model for purposes of comparison with the neural network method detailed
above. It utilizes the same basic idea as presented in \Cref{fig:translation}:
it only differs in the type of transformation used to map between the two
monolingual vector spaces. Whereas our approach uses a deep neural network, this
linear model builds a linear transformation between the two spaces. Given
source-language and target-language training data matrices $W_E, W_F$ (where the
$i$th columns of the two matrices are the vector word representations
corresponding to the $i$th training pair) we assert the existence of a
translation matrix $A$, where $W_F = AW_E$.

We compute the linear transformation by taking $A = W_F W_E^+$, where $W_E^+$ is
the Moore-Penrose pseudoinverse of $W_E$. It is necessary to use the
pseudoinverse of $W_E$, as the matrix is unlikely to be square and invertible.
Then given any source-language word vector $w_e$, we calculate the transformed
target-language word vector as $w_f = A w_e$.

@@

\begin{table*}[htb!]
    \centering
    \small
    \begin{tabular}[t]{l lll}
    \toprule
    Diagnosis & Input & Expected cognate output & Predicted ranked output (translations) \\
    \midrule
    Synonyms & \emph{acceptance} & \emph{aceptación} & \emph{aprobación (approval), \dots} \\
    Near misses & \emph{vanilla} & \emph{vainilla} & \emph{chocolate, vainilla, \dots} \\
    Right neighborhood, wrong spot & \emph{election} & \emph{elección} & \emph{candidato, candidatura (candidacy), \dots} \\
    Alternate sense interpretations & \emph{division} & \emph{división} & \emph{unidad (unit), élite, comando (command), \dots} \\
    \bottomrule
    \end{tabular}
    \caption{Examples of common error patterns observed in the algorithm's output for
        the \bt{Cog} environment}
    \label{tbl:errors}
\end{table*}

>>>>

\newcite{mikolov2013exploiting} found that a linear model could learn a
translation mapping between two monolingual vector spaces. We construct such a
linear model for purposes of comparison with the neural network method detailed
above. It utilizes the same basic idea as presented in \Cref{fig:translation}:
it only differs in the type of transformation used to map between the two
monolingual vector spaces. Whereas our approach uses a deep neural network, this
linear model builds a linear transformation between the two spaces. Given
source-language and target-language training data matrices $W_E, W_F$ (where the
$i$th columns of the two matrices are the vector word representations
corresponding to the $i$th training pair) we assert the existence of a
translation matrix $A$, where
\begin{equation}
  W_F = AW_E.
\end{equation}

We compute the linear transformation by taking $A = W_F W_E^+$, where $W_E^+$ is
the Moore-Penrose pseudoinverse of $W_E$. It is necessary to use the
pseudoinverse of $W_E$, as the matrix is unlikely to be square and invertible.
Then given any source-language word vector $w_e$, we calculate the transformed
target-language word vector as
\begin{equation}
  w_f = A w_e.
\end{equation}

@@

\begin{table*}[htb!]
  \centering
  \resizebox{\linewidth}{!}{
    \begin{tabular}[t]{l lll}
    \toprule
    Diagnosis & Input & Expected cognate output & Predicted ranked output (translations) \\
    \midrule
    Synonyms & \emph{acceptance} & \emph{aceptación} & \emph{aprobación (approval), \dots} \\
    Near misses & \emph{vanilla} & \emph{vainilla} & \emph{chocolate, vainilla, \dots} \\
    Right neighborhood, wrong spot & \emph{election} & \emph{elección} & \emph{candidato, candidatura (candidacy), \dots} \\
    Alternate sense interpretations & \emph{division} & \emph{división} & \emph{unidad (unit), élite, comando (command), \dots} \\
    \bottomrule
    \end{tabular}
  }
  \caption{Examples of common error patterns observed in the algorithm's output for
    the \bt{Cog} environment}
  \label{tbl:errors}
\end{table*}
